\begin{rubric}{Courses}

\entry*[Apr. 2025]
    \textbf{Parallel Computing}
    \newline taught by Dr. Nicolás Wolovick, FAMAF, National University of Córdoba
    \newline Ongoing.
\entry*[Aug. 2024]
    \textbf{Text Mining}
    \newline taught by Dra. Laura Alonso Alemany, FAMAF, National University of Córdoba
    \newline Ongoing.
\entry*[Aug. 2024]
    \textbf{Neural Networks}
    \newline taught by Dr. Francisco Tamarit, FAMAF, National University of Córdoba
    \newline Final Score: 10 out of 10
\entry*[May. 2025]
    \textbf{Introduction to Software Testing}
    \newline taught by Dr. Andrea Bombarda
    \newline Ongoing.
\entry*[Mar. 2025] 
    \textbf{Advances in Automatic Software Testing}
    \newline taught by Dr. Mike Papadakis, Río 2025 Summer School
    \newline Final Score: 9 out of 10
\entry*[Mar. 2025] 
    \textbf{Introduction to Input Grammar Fuzzing}
    \newline taught by Dr. Andreas Zeller, Río 2025 Summer School
    \newline Final Score: 10 out of 10
\entry*[Mar. 2025] 
    \textbf{Analysis of mobile apps for quality and trustworthiness}
    \newline taught by Dr. Alessandra Gorla, Río 2025 Summer School
    \newline Final Score: 10 out of 10
\entry*[Feb. 2024] 
    \textbf{Dynamic Modal Logics}
    \newline taught by Dr. Raul Fervari and Dr. Carlos Areces, Río 2024 Summer School
    \newline Final Score: 6 out of 10
\entry*[Feb. 2024] 
    \textbf{Verification of Fault Trees}
    \newline taught by Dr. Joost-Pieter Katoen, Río 2024 Summer School
\entry*[Aug. 2023] 
    \textbf{Advanced Data Structures}
    \newline taught by Dr. Conrado Martínez, ECI 2023
    \newline Final Score: 10 out of 10
\entry*[Aug. 2023] 
    \textbf{Fuzzing for Compiler Testing}
    \newline taught by Dr. Guillermo Polito, ECI 2023
    \newline Final Score: 9 out of 10
\entry*[Feb. 2023] 
    \textbf{Modeling and Analyzing Concurrent Systems}
    \newline taught by Dr. Thomas Noll, Río 2023 Summer School
    \newline Final Score: 8 out of 10
\entry*[Feb. 2023] 
    \textbf{Formal Approaches to Decision-Making under Uncertainty}
    \newline taught by Dr. Arnd Hartmanns, Río 2023 Summer School
\entry*[Aug. 2022] 
    \textbf{Introduction to APIs}
    \newline taught by Dr. Guido De Caso, ECI 2022
    \newline Final Score: 8 out of 10
\entry*[Aug. 2022] 
    \textbf{Satellite Images Processing}
    \newline taught by Dr. Rafael Grimson, ECI 2022
    \newline Final Score: 7 out of 10
\entry*[Oct. 2019] 
    \textbf{Software Testing}
    \newline taught by Dr. Nazareno Aguirre, CACIC 2019
    \newline Final Score: 10 out of 10
\entry*[2011--2016] 
    \textbf{English Academy} 
    \newline Instituto Superior de Lengua Inglesa (ISLI), Villa Mercedes, San Luis

\end{rubric}